\singlespacing \vspace{-1.6cm} \LARGE Covariation among reproductive traits in flowering plants determine interactions with floral visitors

### 2022-06-23 Manuscript/Lanuza_et_al_2022.Rmd
edits

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[skip=3pt]{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{setspace}
- \usepackage{titlesec}
- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
- \usepackage[style=nature]{biblatex}
- \usepackage[labelformat = empty]{caption}
- \usepackage{pdflscape}
- \usepackage[T1]{fontenc}
- \DeclareUnicodeCharacter{0301}{*************************************}
- \DeclareUnicodeCharacter{1EF3}{*************************************}
---

@@

\textbf{Jose B. Lanuza$^{1,2}$} [barragansljose\@gmail.com](mailto:barragansljose@gmail.com){.email}, \textbf{Romina Rader$^{1}$} [rrader\@une.edu.au](mailto:rrader@une.edu.au){.email}, \textbf{Jamie Stavert$^{3}$} [jamie.stavert\@gmail.com](mailto:jamie.stavert@gmail.com){.email}, \textbf{Liam K. Kendall$^{4}$} [liam.k.kendall\@gmail.com](mailto:liam.k.kendall@gmail.com){.email}, \textbf{Manu E. Saunders$^{1}$} [Manu.Saunders\@une.edu.au](mailto:Manu.Saunders@une.edu.au){.email} \textbf{and Ignasi Bartomeus$^{2}$} [nacho.bartomeus\@gmail.com](mailto:nacho.bartomeus@gmail.com){.email}

@@

**Data accessibility.** All data and code used to conduct this study is deposited at Zenodo

>>>>

header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage[skip=3pt]{caption}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{setspace}
- \usepackage{titlesec}
- \titlespacing{\title}{0pt}{\parskip}{-\parskip}
- \usepackage[style=nature]{biblatex}
- \usepackage[labelformat = empty]{caption}
- \usepackage{pdflscape}
- \usepackage[T1]{fontenc}
- \DeclareUnicodeCharacter{0301}{*************************************}
- \DeclareUnicodeCharacter{1EF3}{*************************************}
- \usepackage{orcidlink}

---

@@

\textbf{Jose B. Lanuza$^{1,2}$} \orcidlink{0000-0002-0287-409X}, \textbf{Romina Rader$^{1}$} \orcidlink{0000-0001-9056-9118}, \textbf{Jamie Stavert$^{3}$} \orcidlink{0000-0002-2103-5320}, \textbf{Liam K. Kendall$^{4}$} \orcidlink{0000-0002-0671-0121}, \textbf{Manu E. Saunders$^{1}$} \orcidlink{0000-0003-0645-8277}
\textbf{and Ignasi Bartomeus$^{2}$}
\orcidlink{0000-0001-7893-4389}

@@

**Data accessibility.** All data and code used to conduct this study is available at Zenodo (https://doi.org/10.5281/zenodo.6705621) and Github (https://github.com/JoseBSL/Reproductive-traits).
